\documentclass[12pt]{article}
\usepackage{ctex}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{nameref}
\usepackage{fancyhdr}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,float}
\usepackage{physics}
\usepackage{pgfplots}
\usepackage[a4paper, total={6in, 9in}]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyhf[HL]{中四 青松下考2122 翻譯試題}
\fancyhf[CF]{\thepage}

\newcommand{\innerprod}[2]{\langle{#1},{#2}\rangle}
\newcommand{\id}{\mathtt{id}}

\begin{document}
    \begin{enumerate}
        \item Simplify $\dfrac{(a^4b^{-3})^5}{a^{-4}b^7}$ and express your answer with positive indices.
        \item Make $h$ to be the subject of $3k=\dfrac{4-5h}{h+2}$.
        \item Factorize\begin{enumerate}
            \item $3a^2-5ab-2b^2$,
            \item $3a^2-5ab-2b^2-3a-b$.
        \end{enumerate}
        \item The cost of a fan is \$300. When the fan is sold, the profit percentage is 26\%.\begin{enumerate}
            \item Find the selling price of the fan.
            \item If the fan is sold at a discount of 30\%, find the marked price.
        \end{enumerate}
        \item Solve $5^\frac{x}{2}=125$.
        \item In $\triangle ABC$, if $AB=5$ cm, $BC=6$ cm, $\angle ABC=20^\circ$, find $AC$.
        \item Let $ABCD$ be a parallelogram, if $AB=8$ cm, $BC=12$ cm, and $\angle ABC=140^\circ$, find the area of $ABCD$.
        \item Solve $x^6+63x^3-64=0$.
        \item Solve for $0^\circ \leq  x \leq 360^\circ$.\begin{enumerate}
            \item $\tan{x}=1$.
            \item $3\sin^2{x}-7\sin{x}-6=0$.
        \end{enumerate}
        \item Simplify $\dfrac{a^{-2}}{(\sqrt{a}b)^3}\times\dfrac{\sqrt[3]{b^4}}{\sqrt{a}}$ and express your answer with positive indices.
        \item It is known that $\log_3{2}=p$ and $\log_3{5}=q$, express the following  log using $p$ and $q$.\begin{enumerate}
            \item $\log_3{10}$.
            \item $\log_3{\dfrac{15}{2}}$.
        \end{enumerate}
        \item Simplify $\dfrac{6}{k-18}+\dfrac{2}{5k+6}$.
        \item It is known that $f(x)=2x^3-19x^2+kx+21$ is divisible by $x-3$.\begin{enumerate}
            \item find the value of $k$.
            \item Hence, factorize $f(x)$.
        \end{enumerate}
        \item It is known that $\begin{cases}
            y=kx^2-8x+2\\
            10x-y-7=0
        \end{cases}$ has only one real root.\begin{enumerate}
            \item find the value of $k$.
            \item Solve the system of equations.
        \end{enumerate}
        \item Suppose $L_2$ is perpendicular to $L_1:5x-4y-20=0$ and passes through $P(-3,1.5)$. $L_1$ and $L_2$ cut x-axis at $B$ and $C$ respectively.\begin{enumerate}
            \item Find the slope of $L_1$. Hence, find the slope of $L_2$.
            \item Find the equation of $L_2$.
            \item Find the intersection point of $L_1$ and $L_2$.
        \end{enumerate}
        \item Let $BCDE$ be a quadrilateral, and $A$ be a point on $ED$, such that $AE=10$ cm, $AD=12$ cm, $EB=8$ cm, $\angle AEB=75^\circ$, $CD=9$ cm and $\angle CDA=82^\circ$.\begin{enumerate}
            \item Find $AB$.
            \item Find $\angle EAB$.
            \item Find the area of $\triangle ABC$.
        \end{enumerate}
        \item Ken spent \$500 to buy some bottles of milk, 10 of them were broken during the transportation. If he sells the remaining for \$4 each, then the profit will be \$60. How many bottles of milk did he buy?
        \item Suppose the relation between $y$ and $\log{x}$ can be represented by $y=k\log{x}+n$, where $k,n$ are constants. Further suppose the graph of the equation passes through $(0,4)$ and $(4,6)$.\begin{enumerate}
            \item Find the value of $k$ and $n$.
            \item Find $x$ in terms of $y$.
        \end{enumerate}
    \end{enumerate}
\end{document}